Subject-specific curves for time series forecasting of smart meter demand

### 2020-01-28 sscts-paper-1-monash.Rmd
Add copy of paper to be used as monash working paper.

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  fig.align = "center",
  message = FALSE,
  warning = FALSE,
  cache = TRUE,
  cache.lazy = FALSE,
  # dev = "pdf",
  dev = "png",
  dpi = 200,
  fig.height = 5 * 1.4,
  fig.width = 8 * 1.4
)
library(tidyverse)
library(tsibble)
library(furrr)
library(lubridate)
library(stringr)
library(lme4)
# library(nlme)
library(splines)
library(forecast)
library(leaps)
source("R/load-data.R")
source("R/feature-selection.R")
source("R/test-models.R")
source("R/models-lme4.R")
source("R/plot-helpers.R")
```

>>>>

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  fig.align = "center",
  message = FALSE,
  warning = FALSE,
  cache = FALSE,
  cache.lazy = FALSE,
  # dev = "pdf",
  dev = "png",
  dpi = 200,
  fig.height = 5 * 1.4,
  fig.width = 8 * 1.4
)
library(tidyverse)
library(tsibble)
library(furrr)
library(lubridate)
library(stringr)
library(lme4)
# library(nlme)
library(splines)
library(forecast)
library(leaps)
source("R/load-data.R")
source("R/feature-selection.R")
source("R/test-models.R")
source("R/models-lme4.R")
source("R/plot-helpers.R")
```
